% Thanks USENIX
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}

% if then else
\usepackage{etoolbox}

% floats and fancy boxes
\usepackage{subcaption}
\usepackage{fancyvrb}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{arydshln}

% babel
\usepackage[english]{babel}

% math symbols
\usepackage{amsmath}
\DeclareMathOperator*{\eq}{==}
\usepackage{amssymb}
\usepackage{ulem}
\normalem
\usepackage{array}
\usepackage{graphicx}

% for better ending page formating
\usepackage{balance}

% for pretty-printing URLs
\usepackage[hyphens]{url}

% algorithm blocks
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

% colors
\usepackage{color}
\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc

% code snippets
\usepackage{listings}
% \renewcommand{\lstlistingname}{Snippet}
\lstset{language=Java,
basicstyle=\ttfamily \footnotesize,
columns=fullflexible,
keywordstyle=\color{javapurple}\bfseries,
stringstyle=\color{javared},
commentstyle=\color{javagreen},
morecomment=[s][\color{javadocblue}]{/**}{*/},
stepnumber=1,
%numbers=left,
numbersep=3pt,
tabsize=4,
showspaces=false,
showstringspaces=false,
captionpos=b
}

% my favs
\newcommand{\p}{Project\-Name}
\newcommand{\cameraready}[2]{#1} % change to #2 for camera ready
\newcommand{\comments}[1]{}
\newcommand{\fixme}[1]{{\bf FIXME: #1}}

\begin{document}

\date{}

\title{\Large \bf Wonderful : A Terrific Application and Fascinating Paper}

\author{
{\rm Mingyuan Xia}\\
McGill University\\
mingyuan.xia@mail.mcgill.ca\\
http://mxia.me
%\and
} % end author

\maketitle

\cameraready{}{
\thispagestyle{empty}
}

\subsection*{Abstract}
Your Abstract Text Goes Here.  Just a few facts.
Whet our appetites.

\section{Introduction}

A paragraph of text goes here.  Lots of text.  Plenty of interesting
text. \\

More fascinating text. Features\endnote{Remember to use endnotes, not footnotes!} galore, plethora of promises.\\

Packages are available at CTAN~\cite{greenwade93}.
\cameraready{}{
\section{Acknowledgments}

A polite author always includes acknowledgments.  Thank everyone,
especially those who funded the work. 
}

\balance
{\footnotesize \bibliographystyle{acm}
\bibliography{example}}


\theendnotes

\end{document}
